A Reduced Order Model for Porous Media Flows: Coupling Linear Regression with Principal Component Analysis (PCA) using High-Order Singular Value Decomposition (HOSVD) in Upscaling Calculations for Permeability in Reservoir Simulations

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
updates

The BaseCase permeability model used here retains the checkerboard desgined used by the recently named authors. Albeit, the permeability dataset for each block in the set of diagonally opposite blocks have similar value (\ie not exactly the same as in the papers referred to), although one set can still be referred to as a set of high permeability blocks while the other set is referred to as a set of low permeability blocks. Furthermore, within each block, the permeability field varies within a pre-defined range and consists of $1600$ permeability values. More details on the design of the permeability field for the BaseCase is described in Section~\ref{subsubsection:basecase_preprocess_algorithm}. Figures~\ref{fig:PermFields}a and~\ref{fig:PermFields}b give a pictorial representation of the permeability field for the base case with the mesh discretization visible and invisible, respectively.  Using the labelling scheme used by \citet{dawe_2008}, the quadrant model block $K1,~K2,~K3$ and $K4$ are top left, bottom left, top right and bottom right, respectively.

>>>>

The BaseCase permeability model used here retains the checkerboard desgined used by these references. Albeit, the permeability dataset for each block in the set of diagonally opposite blocks have similar value (\ie not exactly the same as in the papers referred to). %, although one set can still be referred to as a set of high permeability blocks while the other set is referred to as a set of low permeability blocks.
Furthermore, within each block, permeability dataset varies within a pre-defined range and consists of $1600$ permeability values. More details on the design of the permeability field for the BaseCase is described in Section~\ref{subsubsection:basecase_preprocess_algorithm}. Figures~\ref{fig:PermFields}a-b are pictorial representations of the permeability dataset for the base case with the mesh discretization visible and invisible, respectively.  Using the labelling scheme used by \citet{dawe_2008}, the quadrant model block $K1,~K2,~K3$ and $K4$ are top left, bottom left, top right and bottom right, respectively.
